Enhanced proximity effect in zigzag-shaped Majorana Josephson junctions.

### 2019-02-26 paper/snakemajoranas.tex
rewrite last paragraph of Sec IV

\comment{In a zigzag geometry Majoranas are localized within one segment of zigzag.}
We observe that for zigzag systems the Majorana properties improve.
All of the zigzag type geometries display a reduced coherence length, and the delocalized nature of the wave functions is improved, as is visible through the density plots.
Quantitatively, the improvement in the localization of the Majoranas is also distinctly apparent: the energies of the Majorana states are three orders of magnitude lower than the topological gap.
As mentioned in section \ref{sec:band_structures}, this can be attributed to the way the energy gap and velocity factor into the Majorana coherence length which scales with these parameters $\xi_\textrm{M}=\hbar v_\textrm{F} / \Delta_\textrm{ind}$.  % TODO: make this an Eq? And Replace Delta_ind by E_gap?
Additionally, the reduction of the Majorana size allows for shorter systems sizes, which is favorable because in an experimental device the coherence length of a material sets a limit for the device size.

\comment{The specific geometry is not important.}
The shape of the wave functions does not change significantly depending on the details of the geometry.
The sharp corners of the sawtooth versus the smooth shape of the snakelike system do not have a significant impact on the shape of the wave function, and neither do the disordered edges affect the relevant parameters.

>>>>

\comment{In a zigzag geometry Majoranas are localized within one segment of zigzag independent of details}
We observe that for zigzag systems the Majorana properties improve independent of the details of the specific geometry.
All of the zigzag type geometries display a significantly reduced Majorana size which improves the localization of the Majorana wave functions as is visible in the density plots.
The Majorana size $\xi_\textrm{M}$ improves by a factor ~70 and is localized within one segment of the zigzag.
Further, the topological gap is an order of magnitude lower, and as mentioned in section \ref{sec:band_structures}, this can be attributed to the way the energy gap and velocity factor into the Majorana coherence length which scales with these parameters $\xi_\textrm{M}=\hbar v_\textrm{F} / \Delta_\textrm{ind}$.
Additionally, the reduction of the Majorana size allows for shorter systems sizes, which is favorable because in an experimental device the coherence length of a material sets a limit for the device size.
